Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-04-21 analysis/paper/paper.qmd
CV plots for each variables

cv_aft <- round(cv(data_aft$min_tcsa),2)

@@

>>>>

cv_aft <- round(cv(data_aft$min_tcsa),2)
```

@@

```
```{r}

###### regression of CV with sample size ####

####combine all four variables ###

library(dplyr)
library(purrr)

# Define the list of data frames to be joined
dfs <- list(tcsa_site_ass, tcsa_raw, points_in_veg_zones_all, points_in_veg_zones_forest)

# Define the common key column for joining
join_col <- "min_tcsa"

# Use reduce() to iteratively join the data frames
tcsa_all <- reduce(dfs, left_join, by = join_col) %>%
            dplyr::select(age_ka.x, min_tcsa, Assemblage.x, raw_materials_top.x, ecoregion, Zone) %>%             mutate(mis_stage = case_when (age_ka.x > 26.5 ~ 'Before' , age_ka.x > 19 ~ 'LGM', age_ka.x < 19 ~ 'After'))

# Calculate the CV for each group : LGM stage

tcsa_all_stage <- tcsa_all%>%
  dplyr::group_by(mis_stage) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

tcsa_all_stage$mis_stage <- factor(tcsa_all_stage$mis_stage, levels = c("Before", "LGM", "After"))

tcsa_all_stage_plot <- ggplot(tcsa_all_stage, aes(x = CV, y = sample_size, color = mis_stage)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each period")+
  theme(legend.key.size = unit(0.2, 'cm'), #change legend key size
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.title = element_text(size=4), #change legend title font size
        legend.text = element_text(size=2)) #change legend text font size

# Calculate the CV for each group : raw materials

tcsa_all_raw <- tcsa_all %>% 
    dplyr::group_by(raw_materials_top.x) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

tcsa_all_raw_plot <- ggplot(tcsa_all_raw, aes(x = CV, y = sample_size, color = raw_materials_top.x)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each raw material")+
  theme(legend.key.size = unit(0.2, 'cm'), #change legend key size
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.title = element_text(size=4), #change legend title font size
        legend.text = element_text(size=2)) #change legend text font size

# Calculate the CV for each group : assemblages

tcsa_all_ass <- tcsa_all %>% 
    dplyr::group_by(Assemblage.x) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

tcsa_all_ass_plot <- ggplot(tcsa_all_ass, aes(x = CV, y = sample_size, color = Assemblage.x)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each asseblage(Location)") +
  theme(legend.key.size = unit(0.2, 'cm'), #change legend key size
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.title = element_text(size=4), #change legend title font size
        legend.text = element_text(size=2)) #change legend text font size

# Calculate the CV for each group : vegetation zone

tcsa_all_veg <- tcsa_all %>% 
    dplyr::group_by(ecoregion) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

tcsa_all_veg_plot <- ggplot(tcsa_all_veg, aes(x = CV, y = sample_size, color = ecoregion)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each vegetation zone")+
  theme(legend.key.size = unit(0.2, 'cm'), #change legend key size
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.title = element_text(size=4), #change legend title font size
        legend.text = element_text(size=2)) #change legend text font size

# Calculate the CV for each group : geographic zone

tcsa_all_geo <- tcsa_all %>% 
    dplyr::group_by(Zone) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

tcsa_all_geo_plot <- ggplot(tcsa_all_geo, aes(x = CV, y = sample_size, color = Zone)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each geographic zone")+
  theme(legend.key.size = unit(0.2, 'cm'), #change legend key size
        legend.key.height = unit(0.2, 'cm'), #change legend key height
        legend.key.width = unit(0.2, 'cm'), #change legend key width
        legend.title = element_text(size=4), #change legend title font size
        legend.text = element_text(size=2)) #change legend text font size

plot_grid(  tcsa_all_stage_plot,
  tcsa_all_raw_plot,
tcsa_all_ass_plot,
 tcsa_all_veg_plot, 
  tcsa_all_geo_plot,
ncol =2,
label_size = 1)
